Stability in human interaction networks: primitive typology of vertex, prominence of measures and activity statistics

### 2015-03-31 paper.tex
arrumado mais um pouco a intro

The present work is aimed at finding common and stable characteristics among (email) interaction networks. This includes observations along time, which imply network evolution, a field that has received attention from the research community
for more than a decade~\cite{barabasiEvo,newmanEvolving}.
We consider only directed, weighted and human interaction networks. Undirected and unweighted representations of such networks are also found in the literature and can be obtained by simplification~\cite{GMANE2}.
Meaningful measures depend heavily on the model and system characteristics~\cite{newmanStru, newmanWeight}, therefore the characterization is restricted to most basic metrics of centrality, clustering and symmetry.

@@

This work approaches network stability through temporal evolution observation.
The evolution is represented by a timeline of activity snapshots with a constant number of contiguous messages. These snapshots yield a succession of networks. This approach, although coherent and intuitive, seems not to be explored to date~\cite{netWindowEvo}.

>>>>

Reports on complex networks are usually focused on a particular measure or functionality, such
as accessibility measure or detecting communities~\cite{access,newmanModularity}. Although there are research on networks arisen from specific phenomena, such as social or protein networks, there are few attempts for a general characterization and even less endeavors that take in account the temporal dynamic.

The present work is aimed at finding common and stable characteristics among (email) interaction networks. This is achieved through observations along time, which imply network evolution, a field that has received attention from the research community
for more than a decade~\cite{barabasiEvo,newmanEvolving}. The evolution is represented herein by a timeline of activity snapshots with a constant number of contiguous messages. These snapshots yield a succession of networks. This approach, albeit coherent and intuitive, seems not to be explored to date~\cite{netWindowEvo}.

We consider only directed, weighted and human interaction networks. Undirected and unweighted representations of such networks are also found in the literature and can be obtained by simplification~\cite{GMANE2}.
Meaningful measures depend heavily on the model and system characteristics~\cite{newmanStru, newmanWeight}, therefore the most basic (and ubiquitous, and fundamental) metrics of centrality, clustering and symmetry are analyzed altogether in principal components formation.

@@
